---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "80%"
)
```
# berlingeo

<!-- badges: start -->
<!-- badges: end -->

This package contains spatial data files for various administrative boundaries in Berlin, Germany and currently one function `sf_fisbroker` to convert WKS files from the Berlin Geodata Portal [“FIS-Broker"](https://www.stadtentwicklung.berlin.de/geoinformation/fis-broker/) in sf objects. I was motivated by the package [nycgeo](https://github.com/mfherman/nycgeo) from Matt Herman.

Data Source: Amt für Statistik Berlin-Brandenburg, Data Licence: Lizenz CC-BY-3.0

## Installation

Development version from GitHub

```{r devel-install, eval = FALSE}
remotes::install_github("patperu/berlingeo")
library("berlingeo")
```

```{r}

library(berlingeo)
library(sf)
library(tidyverse)

```

## LOR - Prognoseraum

```{r}

glimpse(lor_pgr_sf)

ggplot(lor_pgr_sf) +
  geom_sf() + 
  theme_minimal()

```

## LOR - Bezirksregion

```{r}

glimpse(lor_bzr_sf)

ggplot(lor_bzr_sf) +
  geom_sf() + 
  theme_minimal()

```

## LOR - Planungsraum

```{r}

glimpse(lor_plr_sf)

ggplot(lor_plr_sf) +
  geom_sf() + 
  theme_minimal()

```

## Convert WKS dataset to a sf (simple features) object

```{r}

sf_fisbroker("s_erhaltgeb_es") %>%
  ggplot() +
    geom_sf() + 
    theme_minimal()

```

Please note that the 'berlingeo' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.

